---
title: "Music Insights"
author: "Michael Messmer"
output:
  html_document:
    df_print: paged
---

First, we need to use the tidyverse library for importing and manipulating our data.

```{r results="hide"}
install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library("tidyverse")

survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

Some of these column names are pretty bad, so let's make them more consistemt.

```{r}
colnames(survey)[colnames(survey) == "Timestamp"] <- "time_submitted"
bad <- "First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"
colnames(survey)[colnames(survey) == bad] <- "pseudonym_generator"
colnames(survey)[colnames(survey) == "What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey) == "Sex"] <- "sex"
colnames(survey)[colnames(survey) == "Major"] <- "academic_major"
colnames(survey)[colnames(survey) == "Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey) == "Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey) == "Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
colnames(survey)[colnames(survey) == "Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey) == "Song"] <- "favorite_song"
colnames(survey)[colnames(survey) == "Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
colnames(preferences)[colnames(preferences) == "Timestamp"] <- "time_submitted"
colnames(preferences)[colnames(preferences) == "What was your pseudonym?"] <- "pseudonym"
```

Now let's load some libraries for tidying the data.

```{r message=FALSE}
library("dplyr")
library("tidyr")
```

Now let's create a "person" table that describes each person from the survey.

```{r}
person <- tibble("time_submitted"=survey$time_submitted, "pseudonym"=survey$pseudonym, "pseudonym_generator"=survey$pseudonym_generator, "sex"=survey$sex, "major"=survey$academic_major, "academic_level"=survey$academic_level, "year_born"=survey$year_born, "favorite_song"=survey$favorite_song)
```

Now let's create a "favorite songs" table that describes the reported favorite songs.

```{r}
favorite_songs <- tibble("pseudonym"=survey$pseudonym, "favorite_song_artist"=survey$favorite_song_artist, "favorite_song"=survey$favorite_song, "favorite_song_link"=survey$favorite_song_link)
```

Now let's create a "ratings" table that describes the rating each person gave each song.

```{r}
ratings <- subset(gather(preferences, "artist_song", "rating", 3:45), select = -c(time_submitted))
```

Now let's standardize the timestamps in our person table.

```{r message=FALSE}
library("readr")
```

```{r}
person$time_submitted <-parse_datetime(person$time_submitted, format="%m/%d/%y %H:%M")
```

Now let's factorize the variables that should be factorized. Major needs to be cleaned slightly so we'll do that as well.

```{r}
person$pseudonym_generator <- as.factor(person$pseudonym_generator)
person$sex <- as.factor(person$sex)
person$major[person$major == "Computer information systems"] <- "Computer Information Systems"
person$major <- as.factor(person$major)
person$academic_level <- as.factor(person$academic_level)
ratings$pseudonym <- as.factor(ratings$pseudonym)
ratings$artist_song <- as.factor(ratings$artist_song)
```

Now our data is ready for analysis.

```{r}
suppressMessages(library(ggplot2))

ratings_plot <- ggplot(data = ratings, aes(rating)) + geom_histogram(bins = 10) + scale_x_continuous(breaks = 1:10)
person_plot <- ggplot(data = ratings, aes(pseudonym, rating)) + geom_boxplot() + labs(x = "Pseudonym", y = "Rating") + theme(axis.text.x=element_text(angle=90, hjust=1))
```

```{r}
joined <- ratings

joined$artist_song <- as.character(joined$artist_song)
joined$artist_song[joined$artist_song == "Arctic Monkeys Arabella"] <- "\tArctic Monkeys Arabella"
joined$artist_song <- str_extract(joined$artist_song, regex("\t(.*)"))
joined$artist_song <- substr(joined$artist_song, start=2, stop=1000000)
joined <- semi_join(joined, person, by=c("pseudonym", "artist_song" = "favorite_song"))
colnames(joined)[colnames(joined) == "artist_song"] <- "favorite_song"

#Assume that duplicates are result of someone using the wrong pseudonym
#Also assume that the higher rating of the favorite song is the true rating
joined <- filter(joined, !(pseudonym=="Band War" & rating==5))
joined <- filter(joined, !(pseudonym=="Angel Angel" & rating==2))
```